### Specialized arrays for climate research
  + Sample data is provided by Web-technology "Aicore  Remote access to AAD archives"
  + <http://aisori.meteo.ru/ClimateR>
#### Iljin Victor, 4.11.2016
```{r my_source, echo=FALSE}
# Before running the script you can uncomment the desired path. Unnecessary comment
source("http://tmeits.github.io/24516/transect/setdw.R")
source("http://tmeits.github.io/24516/transect/clifiles.R")
print(unique(sort(all.code))) 
```
####  Create data.frame - Transect Master Location
  + Draw up a table under the file name and code of station. 
  + Appends the name of the station
```{r master_location, echo=FALSE}

aisoriStattion <- c(
c(20982, 'Volochanka', 70.97, 94.5, 40.2, "SCH3F1.txt"),
c(21908, 'Dzalinda', 70.13, 113.97, 61.9, "SCH451.txt"), 
c(21921, 'Kyusyur', 70.68, 127.4, 33, "SCH511.txt"),
c(23365, 'Sidorovsk', 66.6, 82.5, 34, "SCH512.txt"), 
c(23445, 'Nadym', 65.47, 72.67, 18.8, "SCH513.txt"),
c(24125, 'Olenek', 68.5, 112.43, 207, "SCH591.txt"),
c(24136, 'Suhana', 68.62, 118.33, 76.9, "SCH181.txt"), 
c(24143, 'Dzhardzhan', 68.73, 124, 38.5, "SCH1F1.txt"),  
c(24643, 'Khatyryk-Khoma', 63.95, 124.83, 76.5, "SCH361.txt"),
c(29998, 'Orlik', 52.5, 99.82, 1374.8, "SCH362.txt"),
c(36229, 'Ust-Koksa', 50.27, 85.62, 977.6, "SCH4A1.txt")
)
aisoriStattion.mat <- matrix(aisoriStattion, ncol = 6, byrow = TRUE)
aisoriStattion.df <- as.data.frame(aisoriStattion.mat)
aisoriStattion.df <- setNames(aisoriStattion.df, c("wmo_id", "city", "lat", "lon", "elev_baro", "cli"))
aisoriStattion.df$cli <- as.character(aisoriStattion.df$cli)
aisoriStattion.df$city <- as.character(aisoriStattion.df$city)
aisoriStattion.df$wmo_id <- as.numeric(as.character(aisoriStattion.df$wmo_id))
aisoriStattion.df$lat <- as.numeric(as.character(aisoriStattion.df$lat))
aisoriStattion.df$lon <- as.numeric(as.character(aisoriStattion.df$lon))
aisoriStattion.df$elev_baro <- as.numeric(as.character(aisoriStattion.df$elev_baro))
str(aisoriStattion.df )

```
#### Read and parse the list of files with climate data
  +  Print the number of observations and descriptive statistics from the raw file
  +  Stupidly removed the gaps in the measurements of temperature and precipitation
```{r read_transect_cli}
readAisoriCliFile <- function(url) {
    cli <- read.csv(url, header = FALSE, sep = ";", dec = ".")
    cli <- cli[-c(5, 7, 9, 11, 13, 14)]  # we delete excess columns
    cli <- setNames(cli, c("Station", "Year", "Month", "Day", "TMIN", "TMEAN",
        "TMAX", "PRECIP"))  # Assign columns names
    return(cli)
}
for (i in 1:length(aisoriStattion.df$city)) {
    cliOne <- readAisoriCliFile(paste0(mm_path, "/cli/aisori/", aisoriStattion.df$cli[i]))
    cat("+----------------------", paste0(aisoriStattion.df$wmo_id[i], "-", aisoriStattion.df$city[i]), 
        "----------------------+\n")
    str(cliOne[, c(2, 6, 8)])
    summary(cliOne[, c(2, 6, 8)])
    summary(na.omit(cliOne[, c(2, 6, 8)]))
    str(na.omit(cliOne[, c(2, 6, 8)]))
    
}
```
```{r write_xlsx, echo=FALSE}
Sys.setenv(R_ZIPCMD = paste0(mm_path, "/bin/zip.exe"))  ## path to zip.exe
require(openxlsx)  # # WriteXLSX
for (i in 1:length(aisoriStattion.df$city)) {
    cliOne <- readAisoriCliFile(paste0(mm_path, "/cli/aisori/", aisoriStattion.df$cli[i]))
    newName <- paste0(aisoriStattion.df$wmo_id[i], "-", aisoriStattion.df$city[i], 
        ".aisori.xlsx")
    openxlsx::write.xlsx(cliOne, file = paste0(mm_path, "/cli/aisori/", newName))
}

```

















