### Specialized arrays for climate research
  + Sample data is provided by Web-technology "Aicore - Remote access to AAD archives"
  + <http://aisori.meteo.ru/ClimateR>

#### Iljin Victor, 4.11.2016
```{r my_source, echo=FALSE}
# Before running the script you can uncomment the desired path. Unnecessary comment
rm(list=ls())
source("http://tmeits.github.io/24516/transect/setdw.R")
```
####  Create data.frame - Transect Master Location
  + Draw up a table under the file name and code of station. 
  + Appends the name of the station
```{r master_location, echo=FALSE}

aisoriStattion <- c(c(20982, "Volochanka", 1936, 2015, 70.97, 94.5, 40.2, 
    "SCH3F1.txt"), c(21908, "Dzalinda", 1942, 2015, 70.13, 113.97, 61.9, 
    "SCH451.txt"), c(21921, "Kyusyur", 1909, 2015, 70.68, 127.4, 33, "SCH511.txt"), 
    c(23365, "Sidorovsk", 1959, 1997, 66.6, 82.5, 34, "SCH512.txt"), c(23445, 
        "Nadym", 1959, 2015, 65.47, 72.67, 18.8, "SCH513.txt"), c(24125, 
        "Olenek", 1936, 2015, 68.5, 112.43, 207, "SCH591.txt"), c(24136, 
        "Suhana", 1938, 2015, 68.62, 118.33, 76.9, "SCH181.txt"), c(24143, 
        "Dzhardzhan", 1937, 2015, 68.73, 124, 38.5, "SCH1F1.txt"), c(24643, 
        "Khatyryk-Khoma", 1957, 2015, 63.95, 124.83, 76.5, "SCH361.txt"), 
    c(29998, "Orlik", 1959, 2015, 52.5, 99.82, 1374.8, "SCH362.txt"), 
    c(36229, "Ust-Koksa", 1936, 2015, 50.27, 85.62, 977.6, "SCH4A1.txt"))
aisoriStattion.mat <- matrix(aisoriStattion, ncol = 8, byrow = TRUE)
aisoriStattion.df <- as.data.frame(aisoriStattion.mat)
aisoriStattion.df <- setNames(aisoriStattion.df, c("wmo_id", "city", "beg_year", 
    "end_year", "lat", "lon", "elev_baro", "cli"))
aisoriStattion.df$cli <- as.character(aisoriStattion.df$cli)
aisoriStattion.df$city <- as.character(aisoriStattion.df$city)
aisoriStattion.df$wmo_id <- as.numeric(as.character(aisoriStattion.df$wmo_id))
aisoriStattion.df$beg_year <- as.numeric(as.character(aisoriStattion.df$beg_year))
aisoriStattion.df$end_year <- as.numeric(as.character(aisoriStattion.df$end_year))
aisoriStattion.df$lat <- as.numeric(as.character(aisoriStattion.df$lat))
aisoriStattion.df$lon <- as.numeric(as.character(aisoriStattion.df$lon))
aisoriStattion.df$elev_baro <- as.numeric(as.character(aisoriStattion.df$elev_baro))
str(aisoriStattion.df)

```
#### Read and parse the list of files with climate data
  +  Print the number of observations and descriptive statistics from the raw file
  +  Stupidly removed the gaps in the measurements of temperature and precipitation
```{r read_transect_cli}
readAisoriCliFile <- function(url) {
    cli <- read.csv(url, header = FALSE, sep = ";", dec = ".")
    cli <- cli[-c(5, 7, 9, 11, 13, 14)]  # we delete excess columns
    cli <- setNames(cli, c("Station", "Year", "Month", "Day", "TMIN", "TMEAN",
        "TMAX", "PRECIP"))  # Assign columns names
    return(cli)
}
for (i in 1:length(aisoriStattion.df$city)) {
    cliOne <- readAisoriCliFile(paste0(mm_path, "/cli/aisori/", aisoriStattion.df$cli[i]))
    cat("+----------------------", paste0(aisoriStattion.df$wmo_id[i], "-", aisoriStattion.df$city[i]), 
        "----------------------+\n")
    print(str(cliOne[, c(2, 6, 8)]))
    print(summary(cliOne[, c(2, 6, 8)]))
    #summary(na.omit(cliOne[, c(2, 6, 8)]))
    #str(na.omit(cliOne[, c(2, 6, 8)]))
    
}
```
```{r write_xlsx_csv, echo=FALSE}
write_xlsx_csv <- function() {
    Sys.setenv(R_ZIPCMD = paste0(mm_path, "/bin/zip.exe"))  ## path to zip.exe
    require(openxlsx)  # # WriteXLSX
    for (i in 1:length(aisoriStattion.df$city)) {
        cliOne <- readAisoriCliFile(paste0(mm_path, "/cli/aisori/", aisoriStattion.df$cli[i]))
        newName <- paste0(aisoriStattion.df$wmo_id[i], "_", aisoriStattion.df$city[i], 
            ".", aisoriStattion.df$beg_year[i], "-", aisoriStattion.df$end_year[i])
        openxlsx::write.xlsx(cliOne, file = paste0(mm_path, "/cli/aisori/", 
            newName, ".aisori.xlsx"))
        write.csv2(cliOne, file = paste0(mm_path, "/cli/aisori/", newName, 
            ".aisori.csv"), row.names = FALSE, sep = ";", na = "")
    }
    openxlsx::write.xlsx(aisoriStattion.df, file = paste0(mm_path, "/cli/aisori/", 
        "aisori_station.xlsx"))
    write.csv2(aisoriStattion.df, file = paste0(mm_path, "/cli/aisori/", 
        "aisori_station.csv"), row.names = FALSE)
    
}

# write_xlsx_csv()
```
#### Climatic characteristics calculated on daily data of temperature and precipitation at weather stations transect
```{r clichar, echo=FALSE}
source_clichar <- function() {
    Rmd2R("clichar.Rmd", "clichar.R")
    source("clichar.R")
}
source_clichar()
t1 <- Sys.time()
i <- 4
code <- aisoriStattion.df$wmo_id[i]
cli <- readAisoriCliFile(paste0(mm_path, "/cli/aisori/", aisoriStattion.df$cli[i]))
begy <- aisoriStattion.df$beg_year[i]
endy <- aisoriStattion.df$end_year[i]
P <- cliChar(paste0(code), cli, cli, begy, endy)
P <- na.omit(P[P$StartSG != -9999, ])
cat("Time= ", Sys.time() - t1, "\n")


```
```{r write_char, echo=FALSE}
```




















