### Specialized arrays for climate research
  + Sample data is provided by Web-technology "Aicore - Remote access to AAD archives"
  + <http://aisori.meteo.ru/ClimateR>

#### Iljin Victor, 4.11.2016
```{r my_source, echo=FALSE}
# Before running the script you can uncomment the desired path. Unnecessary comment
rm(list=ls())
source("http://tmeits.github.io/24516/transect/setdw.R")
```
####  Create data.frame - Transect Master Location
  + Draw up a table under the file name and code of station. 
  + Appends the name of the station
```{r master_location, echo=FALSE}

aisoriStattion <- c(c(20982, "Volochanka", 1936, 2015, 70.97, 94.5, 40.2, 
    "SCH3F1.txt"), c(21908, "Dzalinda", 1942, 2015, 70.13, 113.97, 61.9, 
    "SCH451.txt"), c(21921, "Kyusyur", 1909, 2015, 70.68, 127.4, 33, "SCH511.txt"), 
    c(23365, "Sidorovsk", 1959, 1997, 66.6, 82.5, 34, "SCH512.txt"), c(23445, 
        "Nadym", 1959, 2015, 65.47, 72.67, 18.8, "SCH513.txt"), c(24125, 
        "Olenek", 1936, 2015, 68.5, 112.43, 207, "SCH591.txt"), c(24136, 
        "Suhana", 1938, 2015, 68.62, 118.33, 76.9, "SCH181.txt"), c(24143, 
        "Dzhardzhan", 1937, 2015, 68.73, 124, 38.5, "SCH1F1.txt"), c(24643, 
        "Khatyryk-Khoma", 1957, 2015, 63.95, 124.83, 76.5, "SCH361.txt"), 
    c(29998, "Orlik", 1959, 2015, 52.5, 99.82, 1374.8, "SCH362.txt"), 
    c(36229, "Ust-Koksa", 1936, 2015, 50.27, 85.62, 977.6, "SCH4A1.txt"))
aisoriStattion.mat <- matrix(aisoriStattion, ncol = 8, byrow = TRUE)
aisoriStattion.df <- as.data.frame(aisoriStattion.mat)
aisoriStattion.df <- setNames(aisoriStattion.df, c("wmo_id", "city", "beg_year", 
    "end_year", "lat", "lon", "elev_baro", "cli"))
aisoriStattion.df$cli <- as.character(aisoriStattion.df$cli)
aisoriStattion.df$city <- as.character(aisoriStattion.df$city)
aisoriStattion.df$wmo_id <- as.numeric(as.character(aisoriStattion.df$wmo_id))
aisoriStattion.df$beg_year <- as.numeric(as.character(aisoriStattion.df$beg_year))
aisoriStattion.df$end_year <- as.numeric(as.character(aisoriStattion.df$end_year))
aisoriStattion.df$lat <- as.numeric(as.character(aisoriStattion.df$lat))
aisoriStattion.df$lon <- as.numeric(as.character(aisoriStattion.df$lon))
aisoriStattion.df$elev_baro <- as.numeric(as.character(aisoriStattion.df$elev_baro))
str(aisoriStattion.df)

```
#### Read and parse the list of files with climate data
  +  Print the number of observations and descriptive statistics from the raw file
  +  Stupidly removed the gaps in the measurements of temperature and precipitation
  +  Save list dataframe to files
```{r read_transect_cli}
readAisoriCliFile <- function(url) {
    cli <- read.csv(url, header = FALSE, sep = ";", dec = ".")
    cli <- cli[-c(5, 7, 9, 11, 13, 14)]  # we delete excess columns
    cli <- setNames(cli, c("Station", "Year", "Month", "Day", "TMIN", "TMEAN",
        "TMAX", "PRECIP"))  # Assign columns names
    return(cli)
}
for (i in 1:length(aisoriStattion.df$city)) {
    cliOne <- readAisoriCliFile(paste0(mm_path, "/cli/aisori/", aisoriStattion.df$cli[i]))
    cat("+----------------------", paste0(aisoriStattion.df$wmo_id[i], "-", aisoriStattion.df$city[i]), 
        "----------------------+\n")
    print(str(cliOne[, c(2, 6, 8)]))
    print(summary(cliOne[, c(2, 6, 8)]))
    #summary(na.omit(cliOne[, c(2, 6, 8)]))
    #str(na.omit(cliOne[, c(2, 6, 8)]))  
}
# create a list of tables of climate data
cliList <- list()
for (i in 1:length(aisoriStattion.df$city)) {
    cliOne <- readAisoriCliFile(paste0(mm_path, "/cli/aisori/", aisoriStattion.df$cli[i]))
    cat("+----------------------", paste0(aisoriStattion.df$wmo_id[i], "-", aisoriStattion.df$city[i]), 
        "----------------------+\n")
    cliList[[i]] <- na.omit(cliOne[, c(2, 6, 8)])  
}
save(cliList, aisoriStattion.df, file =  paste0(mm_path, "/cli/aisori/aisori-cli-list.Rdata"))
```
```{r write_xlsx_csv, echo=FALSE}
write_xlsx_csv <- function() {
    Sys.setenv(R_ZIPCMD = paste0(mm_path, "/bin/zip.exe"))  ## path to zip.exe
    require(openxlsx)  # # WriteXLSX
    for (i in 1:length(aisoriStattion.df$city)) {
        cliOne <- readAisoriCliFile(paste0(mm_path, "/cli/aisori/", aisoriStattion.df$cli[i]))
        newName <- paste0(aisoriStattion.df$wmo_id[i], "_", aisoriStattion.df$city[i], 
            ".", aisoriStattion.df$beg_year[i], "-", aisoriStattion.df$end_year[i])
        openxlsx::write.xlsx(cliOne, file = paste0(mm_path, "/cli/aisori/", 
            newName, ".aisori.xlsx"))
        write.csv2(cliOne, file = paste0(mm_path, "/cli/aisori/", newName, 
            ".aisori.csv"), row.names = FALSE, sep = ";", na = "")
    }
    openxlsx::write.xlsx(aisoriStattion.df, file = paste0(mm_path, "/cli/aisori/", 
        "aisori_station.xlsx"))
    write.csv2(aisoriStattion.df, file = paste0(mm_path, "/cli/aisori/", 
        "aisori_station.csv"), row.names = FALSE)
    
}

# write_xlsx_csv()
```
#### Climatic characteristics calculated on daily data of temperature and precipitation at weather stations transect
```{r clichar, echo=FALSE}
source_clichar <- function() {
    Rmd2R("clichar.Rmd", "clichar.R")
    source("clichar.R")
}
source_clichar()
t1 <- Sys.time()
result <- list()
limit <- length(aisoriStattion.df$wmo_id)

for (i in 1:limit) {
    cat("+------",aisoriStattion.df$city[i],"------+\n")
    code <- aisoriStattion.df$wmo_id[i]
    cli <- readAisoriCliFile(paste0(mm_path, "/cli/aisori/", aisoriStattion.df$cli[i]))
    begy <- aisoriStattion.df$beg_year[i]
    endy <- aisoriStattion.df$end_year[i]
    P <- cliChar(paste0(code), cli, cli, begy, endy)
    # https://cran.r-project.org/doc/contrib/de_Jonge+van_der_Loo-Introduction_to_data_cleaning_with_R.pdf
    P.na <- na.omit(P[P$StartSG != -9999, ])
    result[[i]] <- P.na  # https://www.r-bloggers.com/concatenating-a-list-of-data-frames/
}

cat("Time= ", Sys.time() - t1, "\n")


```
```{r write_char, echo=FALSE}
writeCharXLSX <- function(listChar) {
    Sys.setenv(R_ZIPCMD = paste0(mm_path, "/bin/zip.exe"))  ## path to zip.exe
    require(openxlsx)  # # WriteXLSX
    for (i in 1:length(aisoriStattion.df$city)) {
        newName <- paste0(aisoriStattion.df$wmo_id[i], "_", aisoriStattion.df$city[i], 
            ".", aisoriStattion.df$beg_year[i], "-", aisoriStattion.df$end_year[i])
        openxlsx::write.xlsx(listChar[i], file = paste0(mm_path, "/cli/aisori/", 
            newName, ".aisori.par.xlsx"))
        write.csv2(listChar[i], file = paste0(mm_path, "/cli/aisori/", newName, 
            ".aisori.par.csv"), row.names = FALSE, sep = ";", na = "")
    }
}
#writeCharXLSX(result)
#openxlsx::write.xlsx(result, file = paste0(mm_path, "/cli/aisori/","aisori.par.xlsx"))
#openxlsx::write.xlsx(transect.par, file = paste0(mm_path, "/cli/aisori/","transect.par.xlsx"))
# save(linearTrends, result, aisoriStattion.df, file =  paste0(mm_path, "/cli/aisori/","aisori.Rdata"))
```
#### 

for each parameter and each station to calculate the linear trend (y=a+bx, where y is a Klim. parameter x-a). Coverage while every station is different. It is necessary to calculate the trends (only need a straight angle nikalna b) for the period from 1970 to the end date of the observations. And form a trail. table (each cell line):
Section code b-b parameter1-parameter2 etc.
```{r trend, echo=FALSE}
# для каждого параметра и каждой станции рассчитать линейный тренд (y=a+bx, где y - клим. параметр, x-год). Время покрытия у всех станций разное. Надо рассчитать тренды (нужен только угол наколна прямой b) за период с 1970 по дату конца наблюдений. И сформировать след. таблицу (каждый участок строка):
# Код участка  b-parameter1 b-parameter2 и т.д.
# .....  .......  ........  ......
# load(file =  paste0(mm_path, "/cli/aisori/","aisori.Rdata"))

# Elapsed days from the beginning of the year
Days <- function(strDate) {
    Y <- as.numeric(format(strDate, "%Y"))
    m <- as.numeric(format(strDate, "%m"))
    d <- as.numeric(format(strDate, "%d"))
    return(num_days(Y, m, d))
}

plotLM <- function(DT, view = FALSE) {
    if (view == TRUE) {
        plot(DT)
        abline(lm(formula = DT$Par ~ DT$Year, data = DT))
        print(summary(lm(formula = DT$Par ~ DT$Year, data = DT)))
    }
}
result1 <- transect.par
#result1 <- result
viewLT <- FALSE

colNames.b <- c("sec_code", "b_STDAT0", "b_STDAT5", "b_FDAT0", "b_FDAT5", 
    "b_INTER0", "b_INTER5", "b_MAXT", "b_MDAT", "b_SUMT0", "b_SUMT5", 
    "b_T220", "b_T225", "b_FT220", "b_FT225", "b_SPEEDT", "b_SUMPREC")
len <-  length(result1)   

linearTrends <- as.data.frame(matrix(0, ncol = 17, nrow = len, byrow = TRUE))
linearTrends <- setNames(linearTrends, colNames.b)

for (i in 1:len) {
    if (i != 23 & i != 25) {
        sti <- as.data.frame(result1[i])
        code <- sti[1, 1]  # code
        linearTrends[i, 1] <- code  # as.numeric
        # Если данные предоставленны позже 1970 берем все sti[1,]$Year
        # sti[1,2]
        if (sti[1, "Year"] >= 1970) {
            sti.trunc <- sti[, 2]
            sti.trunc.all <- sti
        } else {
            sti.trunc <- sti[sti$Year >= 1970, 2]  # the number of years
            sti.trunc.all <- sti[sti$Year >= 1970, ]
        }
        
        
        DT <- data.frame(Year = sti.trunc, Par = sti.trunc.all$INTER0)
        # todo regression can return NA
        DT.lm <- lm(formula = DT$Par ~ DT$Year, data = DT)
        linearTrends[i, "b_INTER0"] <- as.numeric(DT.lm$coefficients[2])
        plotLM(DT, viewLT)
        
        DT <- data.frame(Year = sti.trunc, Par = sti.trunc.all$INTER5)
        DT.lm <- lm(formula = DT$Par ~ DT$Year, data = DT)
        linearTrends[i, "b_INTER5"] <- as.numeric(DT.lm$coefficients[2])
        
        DT <- data.frame(Year = sti.trunc, Par = sti.trunc.all$MAXT)
        DT.lm <- lm(formula = DT$Par ~ DT$Year, data = DT)
        linearTrends[i, "b_MAXT"] <- as.numeric(DT.lm$coefficients[2])
        
        DT <- data.frame(Year = sti.trunc, Par = sti.trunc.all$SUMT0)
        DT.lm <- lm(formula = DT$Par ~ DT$Year, data = DT)
        linearTrends[i, "b_SUMT0"] <- as.numeric(DT.lm$coefficients[2])
        
        DT <- data.frame(Year = sti.trunc, Par = sti.trunc.all$SUMT0)
        DT.lm <- lm(formula = DT$Par ~ DT$Year, data = DT)
        linearTrends[i, "b_SUMT0"] <- as.numeric(DT.lm$coefficients[2])
        
        DT <- data.frame(Year = sti.trunc, Par = sti.trunc.all$SUMT5)
        DT.lm <- lm(formula = DT$Par ~ DT$Year, data = DT)
        linearTrends[i, "b_SUMT5"] <- as.numeric(DT.lm$coefficients[2])
        
        DT <- data.frame(Year = sti.trunc, Par = sti.trunc.all$T220)
        DT.lm <- lm(formula = DT$Par ~ DT$Year, data = DT)
        linearTrends[i, "b_T220"] <- as.numeric(DT.lm$coefficients[2])
        
        DT <- data.frame(Year = sti.trunc, Par = sti.trunc.all$T225)
        DT.lm <- lm(formula = DT$Par ~ DT$Year, data = DT)
        linearTrends[i, "b_T225"] <- as.numeric(DT.lm$coefficients[2])
        
        DT <- data.frame(Year = sti.trunc, Par = sti.trunc.all$FT220)
        DT.lm <- lm(formula = DT$Par ~ DT$Year, data = DT)
        linearTrends[i, "b_FT220"] <- as.numeric(DT.lm$coefficients[2])
        
        DT <- data.frame(Year = sti.trunc, Par = sti.trunc.all$FT225)
        DT.lm <- lm(formula = DT$Par ~ DT$Year, data = DT)
        linearTrends[i, "b_FT225"] <- as.numeric(DT.lm$coefficients[2])
        
        DT <- data.frame(Year = sti.trunc, Par = sti.trunc.all$SPEEDT)
        DT.lm <- lm(formula = DT$Par ~ DT$Year, data = DT)
        linearTrends[i, "b_SPEEDT"] <- as.numeric(DT.lm$coefficients[2])
        
        DT <- data.frame(Year = sti.trunc, Par = sti.trunc.all$SUMPREC)
        DT.lm <- lm(formula = DT$Par ~ DT$Year, data = DT)
        linearTrends[i, "b_SUMPREC"] <- as.numeric(DT.lm$coefficients[2])
        
        # http://www.statmethods.net/input/dates.html
        ds <- as.Date(sti.trunc.all[, 1 + 6], "%d-%m-%Y")
        # https://nsaunders.wordpress.com/2010/08/20/a-brief-introduction-to-apply-in-r/
        DT <- data.frame(Year = sti.trunc, Par = sapply(ds, Days))
        # plot(DT) abline(lm(formula = DT$Par ~ DT$Year, data = DT))
        # print(summary(lm(formula = DT$Par ~ DT$Year, data = DT)))
        DT.lm <- lm(formula = DT$Par ~ DT$Year, data = DT)
        linearTrends[i, "b_STDAT0"] <- as.numeric(DT.lm$coefficients[2])
        
        ds <- as.Date(sti.trunc.all$STDAT5, "%d-%m-%Y")
        DT <- data.frame(Year = sti.trunc, Par = sapply(ds, Days))
        DT.lm <- lm(formula = DT$Par ~ DT$Year, data = DT)
        linearTrends[i, "b_STDAT5"] <- as.numeric(DT.lm$coefficients[2])
        
        ds <- as.Date(sti.trunc.all$FDAT0, "%d-%m-%Y")
        DT <- data.frame(Year = sti.trunc, Par = sapply(ds, Days))
        DT.lm <- lm(formula = DT$Par ~ DT$Year, data = DT)
        linearTrends[i, "b_FDAT0"] <- as.numeric(DT.lm$coefficients[2])
        
        ds <- as.Date(sti.trunc.all$FDAT5, "%d-%m-%Y")
        DT <- data.frame(Year = sti.trunc, Par = sapply(ds, Days))
        DT.lm <- lm(formula = DT$Par ~ DT$Year, data = DT)
        linearTrends[i, "b_FDAT5"] <- as.numeric(DT.lm$coefficients[2])
        
        ds <- as.Date(sti.trunc.all$MDAT, "%d-%m-%Y")
        DT <- data.frame(Year = sti.trunc, Par = sapply(ds, Days))
        DT.lm <- lm(formula = DT$Par ~ DT$Year, data = DT)
        linearTrends[i, "b_MDAT"] <- as.numeric(DT.lm$coefficients[2])
    }  else  linearTrends[i, "sec_code"] <-  -9999
}
linearTrends <- na.omit(linearTrends[linearTrends$sec_code != -9999, ])


linearTrends1 <- linearTrends
       
```
```{r write_linear_trande, echo=FALSE}
write_linear_trande <- function() {
    Sys.setenv(R_ZIPCMD = paste0(mm_path, "/bin/zip.exe"))  ## path to zip.exe
    require(openxlsx)  # # WriteXLSX
    linearTrends1[,2:17] <- round(linearTrends1[,2:17],4)
    openxlsx::write.xlsx(linearTrends1, file = paste0(mm_path, "/cli/aisori/", 
        "linear_trends.aisori.xlsx"))
    write.csv2(linearTrends1, file = paste0(mm_path, "/cli/aisori/", "linear_trends.aisori.csv"), 
        row.names = FALSE, sep = ";", na = "")
}

# write_linear_trande()

```
```{r write_linear_trande_transect, echo=FALSE}
write_linear_trande_transect <- function() {
    Sys.setenv(R_ZIPCMD = paste0(mm_path, "/bin/zip.exe"))  ## path to zip.exe
    require(openxlsx)  # # WriteXLSX
    linearTrends1[,2:17] <- round(linearTrends1[,2:17],4)
    openxlsx::write.xlsx(linearTrends1, file = paste0(mm_path, "/cli/aisori/", 
        "linear_trends.transect.xlsx"))
    write.csv2(linearTrends1, file = paste0(mm_path, "/cli/aisori/", "linear_trends.transect.csv"), 
        row.names = FALSE, sep = ";", na = "")
}

# write_linear_trande_transect()

```



















