
***
### The calculation of the climatic characteristics of daily temperature and precipitation

#### This allowed to characterize each growing season 16-dimensional vector (Shishov V. V. table. 2.7.1, Chapter 2, p. 194)

### Author : Iljin Victor,  Date   : 2/11/2016
***

```{r transect_set_path, echo=FALSE}
source("http://tmeits.github.io/24516/transect/setdw.R")
# mm_path
```
#### Read aisori datasets for test function
#### Work with weather data <http://aisori.meteo.ru/ClimateR> [R]
```{r read_test_cli}

readClimateMinusinsk <- function(url) {
    sm.cli <- read.csv(url, header = FALSE, sep = ";", dec = ".")
    sm.cli <- sm.cli[-c(5, 7, 9, 11, 13, 14)]  # we delete excess columns
    sm.cli <- setNames(sm.cli, c("Station", "Year", "Month", "Day", "TMIN", "TMEAN",
        "TMAX", "PRECIP"))  # Assign columns names
    # 53.42N 91.42E
    Minusinsk.cli <- sm.cli[sm.cli$Station == 29866, ]
    return(Minusinsk.cli)
}
 
Minusinsk.cli <- readClimateMinusinsk(paste0(mm_path, "/SCH231.txt"))

```
#### Helper functions
```{r utility}

#  Reading a specific year, specific weather stations
getCliStation <- function(path, files) {
    D <- read.csv(paste0(path, files), header = FALSE, sep = "", dec = ".")
    D <- setNames(D, c("Day", "Month", "Year", "PRECIP", "TMEAN"))
    return(D)
}
readAisoriCliFile <- function(url) {
    cli <- read.csv(url, header = FALSE, sep = ";", dec = ".")
    cli <- cli[-c(5, 7, 9, 11, 13, 14)]  # we delete excess columns
    cli <- setNames(cli, c("Station", "Year", "Month", "Day", "TMIN", "TMEAN",
        "TMAX", "PRECIP"))  # Assign columns names
    return(cli)
}

# Convert a vector of Year-Month-Day into a string suitable for
# reverse-conversion
date2string <- function(cDate) {
    sD <- paste0(cDate[1], "-", cDate[2], "-", cDate[3])  
    D <- as.Date(sD)  
    return(sD)
}
test_date2string <- function() {
    DS <- date2string(c(2007, 11, 12))
    cat("Convert data as strung= ", DS, "\n")  
}
# test_date2string()

date2string0 <- function(cDate) {
    nDate <- 1:3
    nDate[1] <- cDate[3]
    nDate[2] <- cDate[2]
    nDate[3] <- cDate[1]
    date2string(nDate)
}
test_date2string0 <- function() {
    DS <- date2string0(c(2007, 11, 12))
    cat("Convert data as strung= ", DS, "\n")
}
# test_date2string0()
 
# Reading climatic data in one year
get_one_year <- function(years, now) {
    return(years[years$Year == now, ])
}
test_get_one_year <- function() {
    print(head(get_one_year(Minusinsk.cli, 1964)))
    print(tail(get_one_year(Minusinsk.cli, 1964)))
}
#  test_get_one_year()

# The number of days of observation per year
numberObservation <- function(years, now) {
    Y <- get_one_year(years, now)
    return(length(Y[, 1]))
}
test_numberObservation <- function() {
    cat("numberObservation ", 1964, numberObservation(Minusinsk.cli, 1964), 
        "\n")
}
# test_numberObservation()

# Function retrieves climate data and year for analysis. Returns in a vector the starting date of the observations this year. And end. The format of the text.
periodObservation <- function(years, now, typeData = "DMY") {
    Y <- get_one_year(years, now)
    if (typeData == "DMY") {
        firstDate <- date2string(c(Y[1, ]$Day, Y[1, ]$Month, Y[1, ]$Year))
        lastDate <- date2string(c(Y[length(Y[, ]$Day), ]$Day, Y[length(Y[, ]$Day), 
            ]$Month, Y[length(Y[, ]$Day), ]$Year))
    } else {
        firstDate <- date2string0(c(Y[1, ]$Day, Y[1, ]$Month, Y[1, ]$Year))
        lastDate <- date2string0(c(Y[length(Y[, ]$Day), ]$Day, Y[length(Y[, ]$Day), 
            ]$Month, Y[length(Y[, ]$Day), ]$Year))
    }
    return(c(firstDate, lastDate))
}

test_periodObservation <- function() {
    P <- periodObservation(Minusinsk.cli, 1964)
    cat("periodObservation:", P[1], P[2], "\n")
    altai.files <- list.files(pattern = "\\.txt$", path = "cli/altai", ignore.case = TRUE, 
        recursive = FALSE, full.names = FALSE)
    #print(altai.files)
    CS <- getCliStation(paste0(mm_path, "/cli/altai/"), altai.files[4])
    P <- periodObservation(CS, 1975)
    cat("periodObservation:", P[1], P[2], "\n")
    P <- periodObservation(CS, 1975, typeData = "YMD")
    cat("periodObservation:", P[1], P[2], "\n")
}
# test_periodObservation()

# Assume the beginning of growing season the total transition temperature sumT for 10 consecutive days using a threshold value of 90 degrees Celsius. Then the beginning of the growing season can be considered the first day in this sequence, when conditions will be made (i.e., sumT>=90).
# the beginning of the growing season
seasonBG <- function(years, now, war = TRUE) {
    year <- get_one_year(years, now)
    year <- na.omit(year)
    yearT <- year[, ]$TMEAN
    yearL <- length(yearT)
    for (i in 1:yearL) {
        sumT <- sum(yearT[i:(i + 10)])
        if (!is.na(sumT)) 
            if (sumT >= 90) 
                return(i)
    }
    if (i >= yearL & war == TRUE) {
        warning(paste("Invalid begin day", " Year=", now))
        return(FALSE)
    } else return(FALSE)
    return(i)
}
test_seasonBG <- function() {
    seasonBG(Minusinsk.cli, 1964)
}
# test_seasonBG()
 
# By the end of the growing season to consider the following condition: when the sum of temperatures over 10 consecutive days is below 50 degrees. The end of the season - it's the last day in this sequence.
# the end of the growing season
seasonEG <- function(years, now) {
    year <- get_one_year(years, now)
    year <- na.omit(year)
    yearT <- year[, ]$TMEAN
    yearL <- length(yearT)
    firstDay <- seasonBG(years, now)
    if (firstDay >= yearL) 
        stop("invalid seasonBG day")
    for (i in firstDay:yearL) {
        sumT <- sum(yearT[i:(i + 10)])
        if (!is.na(sumT)) 
            if (sumT < 50) 
                return(i + 10)
    }
    return(i)
}
test_seasonEG <- function() {
    seasonEG(Minusinsk.cli, 1961)
}
# test_seasonEG()

# Beginning and end of the growing season in the specified year
season_growth <- function(data.cli, needYear) {
    return(c(seasonBG(data.cli, needYear), seasonEG(data.cli, needYear)))
}
test_seasonEG <- function() {
    seasonEG(Minusinsk.cli, 1961)
}
# test_seasonEG()

# a function which converts date in number of days from the beginning of the
# year
num_days <- function(year, month, day) {
    D1 <- as.Date(paste(year, "-1-1", sep = ""))
    asd <- as.Date(paste(year, "-", month, "-", day, sep = ""))
    return(as.numeric(difftime(asd, D1, units = "day")))
}
test_season_growth <- function() {
    S64 <- season_growth(Minusinsk.cli, 1964)
    cat("Reading of results season_growth ", S64, "\n")
}
# test_season_growth()

getNumDays <- function(day, month, year) {
    D1 <- as.Date(paste(year, "-1-1", sep = ""))
    asd <- as.Date(paste(year, "-", month, "-", day, sep = ""))
    return(as.numeric(difftime(asd, D1, units = "day")))
}
test_num_days <- function() {
    ND <- num_days(1964, 6, 22)
    cat("num_days=", ND, "\n")
}
test_getNumDays <- function(){
   ND <- getNumDays(22, 6, 1964)
    cat("getNumDay=", ND, "\n")
}
# test_num_days()
# test_getNumDays()

```
### Main functions
       
```{r Main16}
# http://www.tablesgenerator.com/markdown_tables#
# SpeedT is the speed of the temperature rise since the beginning of the growing season until June 22 (the summer solstice). In fact, it is necessary to take daily temperature (time series with daily temperatures) since the beginning of the growing season (e.g. may 25) until June 22 and build for the temperature Tem trend line (i.e. the regression equation of the form=a+bt, where t is day, a and b are regression coefficients). In this case, SpeedT is the same as the coefficient b.
# Speed of rise in temperature
SPEEDT <- function(data.cli, needYear, densityPlot = FALSE) {
    year <- get_one_year(data.cli, needYear)
    year <- na.omit(year)
    sg <- season_growth(data.cli, needYear)
    L <-  sg[1]:num_days(needYear, 6, 22)
    DT <- data.frame(Day = L, Temp = year$TMEAN[L])
    if (densityPlot == TRUE) {
        plot(DT)
        abline(lm(formula = DT$Temp ~ DT$Day, data=DT))
        print(summary(lm(formula = DT$Temp ~ DT$Day, data=DT)))
    }
    DT.lm <- lm(formula = DT$Temp ~ DT$Day, data=DT)
    return(as.numeric(DT.lm$coefficients[2])) # b1
}

# http://www.montefiore.ulg.ac.be/~kvansteen/GBIO0009-1/ac20092010/Class8/Using%20R%20for%20linear%20regression.pdf
# https://ww2.coastal.edu/kingw/statistics/R-tutorials/simplelinear.html
# http://www.rpubs.com/smarcel/106230
# https://www.r-bloggers.com/interpreting-regression-coefficient-in-r/
#https://cran.r-project.org/doc/contrib/Shipunov-rbook.pdf
S <- SPEEDT(Minusinsk.cli, 1969, densityPlot = FALSE)

#cat("SPEED= ", S, "\n")


# The sum of temperatures from 22 June to transition through 0C at the end of
# the season/temperatures from June 22 to transition through 5C at the end of
# the season
FT2205 <- function(data.cli, data.calc, s.year, temp.c = 0) {
    year <- get_one_year(data.cli, s.year)
    year <- na.omit(year)
    sg <- season_growth(data.calc, s.year)
    nd <- num_days(s.year, 6, 22)
    if (length(year[, 1]) < nd) {
        #cat("WARNING: FT2205 num_days= ", nd, "lenYear= ", length(year[, 1]), " \n")
        #cat("WARNING: FT2205 seasonBegin= ", sg[1], "seasonEnd= ", sg[2], " \n")
        warning("the last date of observation is less than the computed end of the growing season")
        nd <- 1
        sg[2] <- length(year[, 1])
    }
    sum_temp <- 0
    for (i in nd:sg[2]) {
        if (year[i, ]$TMEAN > temp.c) {
            sum_temp <- sum_temp + year[i, ]$TMEAN
        }
    }
    return(sum_temp)
}
test_FT2205 <-function(){
    sum_temp0 <- FT2205(Minusinsk.cli, Minusinsk.cli, 1965, 0)
    sum_temp5 <- FT2205(Minusinsk.cli, Minusinsk.cli, 1965, 5)
    cat("FT2205= ", sum_temp0, sum_temp5, "\n")
}
# test_FT2205()

# The sum of temperatures above 0C until June 22/the Sum of temperatures above
# 5C until June 22
T2205 <- function(data.cli, data.calc, s.year, temp.c = 0) {
    year <- get_one_year(data.cli, s.year)
    year <- na.omit(year)
    nd <- num_days(s.year, 6, 22)
    sum_temp <- 0
    if (length(year[, 1]) < nd) {
        # cat("WARNING: T2205 num_days= ", nd, "lenYear= ", length(year[, 1]), " \n")
        warning("june 22 will come after the date of the last observation")
        nd <- length(year[, 1])
    }
    for (i in 1:nd) {
        if (year[i, ]$TMEAN > temp.c) {
            sum_temp <- sum_temp + year[i, ]$TMEAN
        }
    }
    return(sum_temp)
}
if (.TT == TRUE) {
    sum_temp0 <- T2205(Minusinsk.cli, Minusinsk.cli, 1965, 0)
    sum_temp5 <- T2205(Minusinsk.cli, Minusinsk.cli, 1965, 5)
    cat("T2205= ", sum_temp0, sum_temp5, "\n")
}

# The sum of temperatures more 0C - the Sum of temperatures more than 5C
SUMT0 <- function (data.cli, data.calc, s.year, temp.c = 0) {
  year <- get_one_year(data.cli, s.year)
  year <- na.omit(year)
  sum_temp <- 0
  for(i in 1: length(year[, 1])) {
    if(year[i, ]$TMEAN > temp.c) {
      sum_temp <- sum_temp + year[i, ]$TMEAN
    }
  }
  return(sum_temp)
}
# test
sum_temp0 <- SUMT0(Minusinsk.cli, Minusinsk.cli, 1963, 0)
sum_temp5 <- SUMT0(Minusinsk.cli, Minusinsk.cli, 1963, 5)
cat("SUMT0= ", sum_temp0, sum_temp5, "\n")

# The date of transition through 0C-5C at the beginning of the growing season
STDAT0 <- function (data.cli, data.calc, s.year, temp.c = 0) {
  year <- get_one_year(data.cli, s.year)
  year <- na.omit(year)
  sg <- season_growth(data.calc, s.year)
  data.0c <- c(1, 1, 1)
  for(i in 1: length(year[, 1])) {
    if(year[i, ]$TMEAN >= temp.c & i >= sg[1]) {
      data.0c[3] <- year[i, ]$Year
      data.0c[2] <- year[i, ]$Month
      data.0c[1] <- year[i, ]$Day
      return(data.0c)
    }
  }
  stop("In the permafrost, the trees do not grow. Check climatico.")
}
R0 <- STDAT0(Minusinsk.cli, Minusinsk.cli, 1969)
R5 <- STDAT0(Minusinsk.cli, Minusinsk.cli, 1969, temp.c = 11)
cat("STDAT0= ", R0, R5, "\n")

# Date of transition at the end of the season through 0C-5C
FDAT0 <- function (data.cli, data.calc, s.year, temp.c = 0) {
  year <- get_one_year(data.cli, s.year)
  year <- na.omit(year)
  sg <- season_growth(data.calc, s.year)
  data.0c <- c(1, 1, 1)
  for(i in sort(1: length(year[, 1]), decreasing = TRUE)) {
    if(year[i, ]$TMEAN >= temp.c & i <= sg[2]) {
      data.0c[3] <- year[i, ]$Year
      data.0c[2] <- year[i, ]$Month
      data.0c[1] <- year[i, ]$Day
      return(data.0c)
    }
  }
  stop("In the permafrost, the trees do not grow. Check climatico.")
}
R0 <- FDAT0(Minusinsk.cli, Minusinsk.cli, 1969)
R5 <- FDAT0(Minusinsk.cli, Minusinsk.cli, 1969, 5)
cat("FDAT0= ", R0, R5, "\n")

# The duration of the season from 0C to 0C or 5C to 5C
INTER0 <- function(data.cli, data.calc, s.year, temp.c = 0) {
    year <- get_one_year(data.cli, s.year)
    sg <- season_growth(data.calc, s.year)
    lbeg <- STDAT0(data.cli, data.calc, s.year, temp.c)
    lend <- FDAT0(data.cli, data.calc, s.year, temp.c)
    
    startdate <- as.Date(paste(as.character(lbeg[3]), "-", as.character(lbeg[2]), 
        "-", as.character(lbeg[1]), sep = ""))
    enddate <- as.Date(paste(as.character(lend[3]), "-", as.character(lend[2]), 
        "-", as.character(lend[1]), sep = ""))
    # http://distrland.blogspot.ru/2015/04/r-2-date-base-r.html
    days <- as.numeric(difftime(enddate, startdate, units = "day"))
    return(days)
}
I1 <- INTER0(Minusinsk.cli, Minusinsk.cli, 1965, 0)
I2 <- INTER0(Minusinsk.cli, Minusinsk.cli, 1966, 0)
I3 <- INTER0(Minusinsk.cli, Minusinsk.cli, 1969, 5)
cat("INTER0= ", I1, I2, I3, "\n")

# The amount of precipitation during the growing season
SUMPREC <- function(data.cli, data.calc, s.year) {
    new.year <- na.omit(get_one_year(data.cli, s.year))
    sg <- season_growth(data.calc, s.year)
    
    return(sum(new.year$PRECIP[sg[1]:sg[2]]))
}
SP <- SUMPREC(Minusinsk.cli, Minusinsk.cli, 1964)
cat("SUMPREC= ", SP, "\n")

# The maximum temperature
MAXT <- function(data.cli, s.year) {
    TMAX <- data.cli[data.cli$Year == s.year, ]$TMEAN
    TMAX <- na.omit(TMAX)
    return(max(TMAX))
}
MT1 <- MAXT(Minusinsk.cli, 1963)
MT2 <- MAXT(Minusinsk.cli, 1996)
cat("MAXT= ", MT1, MT2, "\n")

# Date of the maximum temperature
MDAT <- function(data.cli, s.year) {
  temp.max <- -99
  data.max <- c(1, 1, 1)
  year <- get_one_year(data.cli, s.year)
  year <- na.omit(year)
  for(i in 1: length(year[, 1])) {
    if(year[i, ]$TMEAN > temp.max) {
      temp.max <- year[i, ]$TMEAN
      data.max[3] <- year[i, ]$Year
      data.max[2] <- year[i, ]$Month
      data.max[1] <- year[i, ]$Day
    }
  }
  #return(list(data.max, temp.max))
  return(data.max)
}
MD <- MDAT(Minusinsk.cli, 1964)
MDS <- date2string(MD)
cat("MDAT= ", MD, MDS, "\n")

```
### Main function cliChar
```{r cliChar}
catE <- function(strg, echo = FALSE) {
    if (echo == TRUE) 
        cat(strg)
}

cliChar <- function(stationCode, data.cli, data.calc, beginYear, endYear) {
    period <- beginYear:endYear  # the calculation of the number of observations 
    l <- length(period)
    # the creation of a matrix of l rows and 16 columns
    m16 <- matrix(c(1:(l * (16 + 6))), nrow = l, ncol = (16 + 6), byrow = TRUE)
    m16.df <- as.data.frame(m16)  #  converted to dataframe
    firstCol <- c("Station_Code", "Year", "ObsBeg","ObsEnd","StartSG", "EndSG")
    lastCol <- c("STDAT0", "STDAT5", "FDAT0", "FDAT5", "INTER0", "INTER5", "MAXT", "MDAT", 
        "SUMT0", "SUMT5", "T220", "T225", "FT220", "FT225", "SPEEDT", "SUMPREC")
    # assign names to the columns
    df16 <- setNames(m16.df, c(firstCol, lastCol))
    # the task is to determine the data type of each column
    df16$Station_Code <- as.character(df16$Station_Code)
    df16$ObsBeg <- as.character(df16$ObsBeg)
    df16$ObsEnd <- as.character(df16$ObsEnd)
    df16$STDAT0 <- as.character(df16$STDAT0)
    df16$STDAT5 <- as.character(df16$STDAT5)
    df16$FDAT0 <- as.character(df16$FDAT0)
    df16$FDAT5 <- as.character(df16$FDAT5)
    df16$MDAT <- as.character(df16$MDAT)
    cat("Start eval16CliPars\n")
    for (i in 1:l) {
        
        # There is the initial year of observation is finite. The intermediate may be
        # missing. Skip the calculation cycle.
        
        # If the beginning of the season it is impossible to calculate a noise. For example,
        # climatic data starts from August and the season is from may
        if ((numberObservation(data.cli, period[i]) > 69) & (seasonBG(data.cli, period[i], war = FALSE) !=
            FALSE)) { # Not displays a warning about the impossibility to calculate the beginning of the growing season if a year is skipped
            
            PO <- periodObservation(data.cli, period[i])
        firstDate <- PO[1]
        lastDate <- PO[2]
        cat("\n\n****** Year:", period[i], "Observation:", numberObservation(data.cli, 
            period[i]), "Period:", firstDate, lastDate, "******\n")
        df16$Station_Code[i] <- stationCode
        df16$Year[i] <- period[i]
            
            df16$ObsBeg[i] <-  firstDate
            df16$ObsEnd[i] <-  lastDate         
            SE <- season_growth(data.cli, period[i])
            if(SE[1] == FALSE) SE[1]<- -9999
            df16$StartSG[i] <- SE[1]
            df16$EndSG[i] <- SE[2]
            catE("The date of transition through 0C at the beginning of the growing season STDAT0\n")
            D <- STDAT0(data.cli, data.calc, period[i])
            df16$STDAT0[i] <- date2string(D)
            catE("The date of transition through 5C in the beginning of the growing season STAT5\n")
            D <- STDAT0(data.cli, data.calc, period[i], 11)
            df16$STDAT5[i] <- date2string(D)
            catE("Date of transition at the end of the season after 0 - 5 FDAT0\n")
            D <- FDAT0(data.cli, data.calc, period[i])
            df16$FDAT0[i] <- date2string(D)
            D <- FDAT0(data.cli, data.calc, period[i], 5)
            df16$FDAT5[i] <- date2string(D)
            catE("The maximum temperature MAXT\n")
            df16$MAXT[i] <- MAXT(data.cli, period[i])
            catE("Date of the maximum temperature MDAT\n")
            D <- MDAT(data.cli, period[i])
            df16$MDAT[i] <- date2string(D)
            catE("The duration of the season from 0C to 0C, 5C to 5C INTER0\n")
            SL <- INTER0(data.cli, data.calc, period[i])
            df16$INTER0[i] <- SL
            df16$INTER5[i] <- INTER0(data.cli, data.calc, period[i], temp.c = 5)
            catE("The sum of temperatures more 0C, 5C SUMT0\n")
            df16$SUMT0[i] <- SUMT0(data.cli, data.calc, period[i])
            df16$SUMT5[i] <- SUMT0(data.cli, data.calc, period[i], 5)
            catE("The sum of temperatures above 0C-5C until June 22 T2205\n")
            df16$T220[i] <- T2205(data.cli, data.calc, period[i])
            df16$T225[i] <- T2205(data.cli, data.calc, period[i], 5)
            catE("The sum of temperatures from 22 June to go through 0o at the end of the season FT2205\n")
            df16$FT220[i] <- FT2205(data.cli, data.calc, period[i])
            df16$FT225[i] <- FT2205(data.cli, data.calc, period[i], temp.c = 5)
            catE("The rate of temperature rise of  SPEEDT\n")
            df16$SPEEDT[i] <- SPEEDT(data.cli, period[i])
            catE("The amount of precipitation during the growing season SUMPREC\n")
            df16$SUMPREC[i] <- SUMPREC(data.cli, data.calc, period[i])
        } else {
            cat("****** Year:", period[i],"\n")
            cat("#################### Skip a year!!!! \n")
            df16$StartSG[i] <- -9999  # Mark the year with a bad climatical
        }
        
    }
    cat("\n")
    # the estimated return table from function
    return(df16)
}

cat("cliChar Done.\n")

```
### Test cliChar
```{r sysadmn}
#
E <- cliChar("23365", Minusinsk.cli, Minusinsk.cli, 2011, 2013)
print(summary(E))

```
### Tips and Trics
```{r tips}
run <- function() {
    Rmd2R("clichar.Rmd", "clichar.R")
    source("clichar.R")
}

#runAllChunks("clichar.Rmd")

# http://pbil.univ-lyon1.fr/Rweb/

# http://www.biostat.jhsph.edu/~rpeng/docs/R-debug-tools.pdf
# http://tukachev.flogiston.ru/blog/?p=1352
# http://r-analytics.blogspot.ru/p/blog-page_20.html#.V_8uqeWLS01
#  http://kpfu.ru/docs/F568269105/metodichka_R_1.pdf
#  http://shelly.kpfu.ru/e-ksu/docs/F1594376599/%ec%e5%f2%ee%e4%e8%f7%ea%e0_R_2.pdf
#  http://herba.msu.ru/shipunov/software/r/cbook.pdf
#  http://gis-lab.info/docs/books/moskalev2010_statistical_analysis_with_r.pdf
#  https://dl.dropboxusercontent.com/u/7521662/Zaryadov%20%282010%29%20Intro%20to%20R.pdf
#  http://www.unn.ru/pages/e-library/methodmaterial/2010/3.pdf
#  http://gis-lab.info/docs/saveliev2012-geostat.pdf
#  http://www.ievbras.ru/ecostat/Kiril/Article/A32/Starb.pdf
#  http://ashipunov.info/shipunov/school/books/rbook.pdf
#  https://dl.dropboxusercontent.com/u/7521662/Saveliev_2014_Code.rar
#  https://dl.dropboxusercontent.com/u/7521662/Saveliev_2014_Point_Process.pdf
#  https://github.com/ranalytics/r-tutorials/tree/master/Edition_2015
#  http://www.ievbras.ru/ecostat/Kiril/R/Ecotox/Ecotoxicology.pdf
#  http://www.ievbras.ru/ecostat/Kiril/R/Ecotox/Scripts_data.zip
#  http://www.inp.nsk.su/~baldin/DataAnalysis/R/R-10-hpc.pdf

```




















