
***
### For each year-written function to calculate the 16 climatic characteristics

#### This allowed to characterize each growing season 16-dimensional vector (Shishov V. V. table. 2.7.1, Chapter 2, p. 194)

### Author : Iljin Victor,  Date   : 31/09/2016
***

```{r transect_set_path}
## Set work path
getOsVersion <- function() {
    sysinf <- Sys.info()
    if (!is.null(sysinf)) 
        osVersion <- sysinf["version"] else stop("mystery machine...")
    return(osVersion)
}
getOsVersion()

# Installation of a working directory
setWorkDir <- function(osVersion) {
    if (osVersion == "build 2600, Service Pack 3") 
        setwd("Z:/home/larisa/Dropbox/24516/transect/")
    else if (osVersion == "#32-Ubuntu SMP Fri Apr 16 08:10:02 UTC 2010")
        setwd("/home/larisa/Dropbox/24516/transect/")
    else if (osVersion == "build 7601, Service Pack 1")
        setwd("C:/Users/IVA/Dropbox/24516/transect/") else stop("mystery...")
    return(getwd())
}
mm_path <- setWorkDir(getOsVersion())
mm_path

```
#### Read test datasets
#### Work with weather data <http://aisori.meteo.ru/ClimateR> [R]
```{r read_test_cli}

readClimateMinusinsk <- function(url) {
    sm.cli <- read.csv(url, header = FALSE, sep = ";", dec = ".")
    sm.cli <- sm.cli[-c(5, 7, 9, 11, 13, 14)]  # we delete excess columns
    sm.cli <- setNames(sm.cli, c("Station", "Year", "Month", "Day", "TMIN", "TMEAN",
        "TMAX", "PRECIP"))  # Assign columns names
    # 53.42N 91.42E
    Minusinsk.cli <- sm.cli[sm.cli$Station == 29866, ]
    return(Minusinsk.cli)
}

Minusinsk.cli <- readClimateMinusinsk(paste0(mm_path, "/SCH231.txt"))
tail(Minusinsk.cli)
str(Minusinsk.cli)
summary(Minusinsk.cli)
sum(is.na(Minusinsk.cli))
mean(is.na(Minusinsk.cli))
```
### Utility functions
```{r utility}

# Reading climatic data in one year
get_one_year <- function(years, now) {
    return(years[years$Year == now, ])
}
Y64 <- get_one_year(Minusinsk.cli, 1964) # test
head(Y64)
summary(Y64[, 5:8])

# Assume the beginning of growing season the total transition temperature sumT for 10 consecutive days using a threshold value of 90 degrees Celsius. Then the beginning of the growing season can be considered the first day in this sequence, when conditions will be made (i.e., sumT>=90).
# the beginning of the growing season
seasonBG <- function(years, now) {
    year <- get_one_year(years, now)
    year <- na.omit(year)
    yearT <- year[, ]$TMEAN
    yearL <- length(yearT)
    for (i in 1:yearL) {
        sumT <- sum(yearT[i:(i + 10)])
        if (!is.na(sumT)) 
            if (sumT >= 90) 
                return(i)
    }
    if (i >= yearL) 
        stop(paste("Invalid begin day", " Year=", now))
    return(i)
}
seasonBG(Minusinsk.cli, 1964)  # test

# By the end of the growing season to consider the following condition: when the sum of temperatures over 10 consecutive days is below 50 degrees. The end of the season - it's the last day in this sequence.
# the end of the growing season
seasonEG <- function(years, now) {
    year <- get_one_year(years, now)
    year <- na.omit(year)
    yearT <- year[, ]$TMEAN
    yearL <- length(yearT)
    firstDay <- seasonBG(years, now)
    if (firstDay >= yearL) 
        stop("invalid seasonBG day")
    for (i in firstDay:yearL) {
        sumT <- sum(yearT[i:(i + 10)])
        if (!is.na(sumT)) 
            if (sumT < 50) 
                return(i + 10)
    }
    return(i)
}
seasonEG(Minusinsk.cli, 1961)  # test

# Beginning and end of the growing season in the specified year
season_growth <- function(data.cli, needYear) {
    return(c(seasonBG(data.cli, needYear), seasonEG(data.cli, needYear)))
}
S64 <- season_growth(Minusinsk.cli, 1964)
cat("Reading of results season_growth ", S64, "\n")

# a function which converts date in number of days from the beginning of the
# year
num_days <- function(year, month, day) {
    D1 <- as.Date(paste(year, "-1-1", sep = ""))
    asd <- as.Date(paste(year, "-", month, "-", day, sep = ""))
    return(as.numeric(difftime(asd, D1, units = "day")))
}
ND <- num_days(1964, 6, 22)
cat("NumDay=", ND, "\n")

getNumDays <- function(day, month, year) {
    D1 <- as.Date(paste(year, "-1-1", sep = ""))
    asd <- as.Date(paste(year, "-", month, "-", day, sep = ""))
    return(as.numeric(difftime(asd, D1, units = "day")))
}
if (.TT == TRUE) cat("getNumDays(1964, 6, 22)= ", getNumDays(1964, 6, 22), "\n")

# Convert a vector of Year-Month-Day into a string suitable for
# reverse-conversion
date2string <- function(cDate) {
    sD <- paste(cDate[1], "-", cDate[2], "-", cDate[3], sep = "")  
    D <- as.Date(sD)  
    return(sD)
}
DS <- date2string(c(2007, 11, 12))
cat("Convert data as strung= ", DS, "\n")

date2string0 <- function(cDate) {
    nDate <- 1:3
    nDate[1] <- cDate[3]
    nDate[2] <- cDate[2]
    nDate[3] <- cDate[1]
    date2string(nDate)
}
if (.TT == TRUE) {
    DS <- date2string0(c(2007, 11, 12))
    cat("Convert data as strung= ", DS, "\n")
}

```
### Main functions
       
```{r Main16}
# http://www.tablesgenerator.com/markdown_tables#
# SpeedT is the speed of the temperature rise since the beginning of the growing season until June 22 (the summer solstice). In fact, it is necessary to take daily temperature (time series with daily temperatures) since the beginning of the growing season (e.g. may 25) until June 22 and build for the temperature Tem trend line (i.e. the regression equation of the form=a+bt, where t is day, a and b are regression coefficients). In this case, SpeedT is the same as the coefficient b.
# Speed of rise in temperature
SPEEDT <- function(data.cli, needYear, densityPlot = FALSE) {
    year <- get_one_year(data.cli, needYear)
    year <- na.omit(year)
    sg <- season_growth(data.cli, needYear)
    L <-  sg[1]:num_days(needYear, 6, 22)
    DT <- data.frame(Day = L, Temp = year$TMEAN[L])
    if (densityPlot == TRUE) {
        plot(DT)
        abline(lm(formula = DT$Temp ~ DT$Day, data=DT))
        print(summary(lm(formula = DT$Temp ~ DT$Day, data=DT)))
    }
    DT.lm <- lm(formula = DT$Temp ~ DT$Day, data=DT)
    return(as.numeric(DT.lm$coefficients[2])) # b1
}

# http://www.montefiore.ulg.ac.be/~kvansteen/GBIO0009-1/ac20092010/Class8/Using%20R%20for%20linear%20regression.pdf
# https://ww2.coastal.edu/kingw/statistics/R-tutorials/simplelinear.html
# http://www.rpubs.com/smarcel/106230
# https://www.r-bloggers.com/interpreting-regression-coefficient-in-r/
#https://cran.r-project.org/doc/contrib/Shipunov-rbook.pdf
S <- SPEEDT(Minusinsk.cli, 1969, densityPlot = TRUE)
S

#cat("SPEED= ", S, "\n")


# The sum of temperatures from 22 June to transition through 0C at the end of
# the season/temperatures from June 22 to transition through 5C at the end of
# the season
FT2205 <- function(data.cli, data.calc, s.year, temp.c = 0) {
    year <- get_one_year(data.cli, s.year)
    year <- na.omit(year)
    sg <- season_growth(data.calc, s.year)
    nd <- num_days(s.year, 6, 22)
    sum_temp <- 0
    for (i in nd:sg[2]) {
        if (year[i, ]$TMEAN > temp.c) {
            sum_temp <- sum_temp + year[i, ]$TMEAN
        }
    }
    return(sum_temp)
}
sum_temp0 <- FT2205(Minusinsk.cli, Minusinsk.cli, 1965, 0)
sum_temp5 <- FT2205(Minusinsk.cli, Minusinsk.cli, 1965, 5)
cat("FT2205= ", sum_temp0, sum_temp5, "\n")

# The sum of temperatures above 0C until June 22/the Sum of temperatures above
# 5C until June 22
T2205 <- function(data.cli, data.calc, s.year, temp.c = 0) {
    year <- get_one_year(data.cli, s.year)
    year <- na.omit(year)
    nd <- num_days(s.year, 6, 22)
    cat("T2205 num_days= ", nd, "lenYear= ", length(year[,1])," \n")
    sum_temp <- 0
    if(length(year[,1]) < nd)
    for (i in 1:nd) {
        if (year[i, ]$TMEAN > temp.c) {
            sum_temp <- sum_temp + year[i, ]$TMEAN
        }
    }
    return(sum_temp)
}
sum_temp0 <- T2205(Minusinsk.cli, Minusinsk.cli, 1965, 0)
sum_temp5 <- T2205(Minusinsk.cli, Minusinsk.cli, 1965, 5)
cat("T2205= ", sum_temp0, sum_temp5, "\n")

# The sum of temperatures more 0C - the Sum of temperatures more than 5C
SUMT0 <- function (data.cli, data.calc, s.year, temp.c = 0) {
  year <- get_one_year(data.cli, s.year)
  year <- na.omit(year)
  sum_temp <- 0
  for(i in 1: length(year[, 1])) {
    if(year[i, ]$TMEAN > temp.c) {
      sum_temp <- sum_temp + year[i, ]$TMEAN
    }
  }
  return(sum_temp)
}
# test
sum_temp0 <- SUMT0(Minusinsk.cli, Minusinsk.cli, 1963, 0)
sum_temp5 <- SUMT0(Minusinsk.cli, Minusinsk.cli, 1963, 5)
cat("SUMT0= ", sum_temp0, sum_temp5, "\n")

# The date of transition through 0C-5C at the beginning of the growing season
STDAT0 <- function (data.cli, data.calc, s.year, temp.c = 0) {
  year <- get_one_year(data.cli, s.year)
  year <- na.omit(year)
  sg <- season_growth(data.calc, s.year)
  data.0c <- c(1, 1, 1)
  for(i in 1: length(year[, 1])) {
    if(year[i, ]$TMEAN >= temp.c & i >= sg[1]) {
      data.0c[3] <- year[i, ]$Year
      data.0c[2] <- year[i, ]$Month
      data.0c[1] <- year[i, ]$Day
      return(data.0c)
    }
  }
  stop("In the permafrost, the trees do not grow. Check climatico.")
}
R0 <- STDAT0(Minusinsk.cli, Minusinsk.cli, 1969)
R5 <- STDAT0(Minusinsk.cli, Minusinsk.cli, 1969, temp.c = 11)
cat("STDAT0= ", R0, R5, "\n")

# Date of transition at the end of the season through 0C-5C
FDAT0 <- function (data.cli, data.calc, s.year, temp.c = 0) {
  year <- get_one_year(data.cli, s.year)
  year <- na.omit(year)
  sg <- season_growth(data.calc, s.year)
  data.0c <- c(1, 1, 1)
  for(i in sort(1: length(year[, 1]), decreasing = TRUE)) {
    if(year[i, ]$TMEAN >= temp.c & i <= sg[2]) {
      data.0c[3] <- year[i, ]$Year
      data.0c[2] <- year[i, ]$Month
      data.0c[1] <- year[i, ]$Day
      return(data.0c)
    }
  }
  stop("In the permafrost, the trees do not grow. Check climatico.")
}
R0 <- FDAT0(Minusinsk.cli, Minusinsk.cli, 1969)
R5 <- FDAT0(Minusinsk.cli, Minusinsk.cli, 1969, 5)
cat("FDAT0= ", R0, R5, "\n")

# The duration of the season from 0C to 0C or 5C to 5C
INTER0 <- function(data.cli, data.calc, s.year, temp.c = 0) {
    year <- get_one_year(data.cli, s.year)
    sg <- season_growth(data.calc, s.year)
    lbeg <- STDAT0(data.cli, data.calc, s.year, temp.c)
    lend <- FDAT0(data.cli, data.calc, s.year, temp.c)
    
    startdate <- as.Date(paste(as.character(lbeg[3]), "-", as.character(lbeg[2]), 
        "-", as.character(lbeg[1]), sep = ""))
    enddate <- as.Date(paste(as.character(lend[3]), "-", as.character(lend[2]), 
        "-", as.character(lend[1]), sep = ""))
    # http://distrland.blogspot.ru/2015/04/r-2-date-base-r.html
    days <- as.numeric(difftime(enddate, startdate, units = "day"))
    return(days)
}
I1 <- INTER0(Minusinsk.cli, Minusinsk.cli, 1965, 0)
I2 <- INTER0(Minusinsk.cli, Minusinsk.cli, 1966, 0)
I3 <- INTER0(Minusinsk.cli, Minusinsk.cli, 1969, 5)
cat("INTER0= ", I1, I2, I3, "\n")

# The amount of precipitation during the growing season
SUMPREC <- function(data.cli, data.calc, s.year) {
    new.year <- na.omit(get_one_year(data.cli, s.year))
    sg <- season_growth(data.calc, s.year)
    
    return(sum(new.year$PRECIP[sg[1]:sg[2]]))
}
SP <- SUMPREC(Minusinsk.cli, Minusinsk.cli, 1964)
cat("SUMPREC= ", SP, "\n")

# The maximum temperature
MAXT <- function(data.cli, s.year) {
    TMAX <- data.cli[data.cli$Year == s.year, ]$TMEAN
    TMAX <- na.omit(TMAX)
    return(max(TMAX))
}
MT1 <- MAXT(Minusinsk.cli, 1963)
MT2 <- MAXT(Minusinsk.cli, 1996)
cat("MAXT= ", MT1, MT2, "\n")

# Date of the maximum temperature
MDAT <- function(data.cli, s.year) {
  temp.max <- -99
  data.max <- c(1, 1, 1)
  year <- get_one_year(data.cli, s.year)
  year <- na.omit(year)
  for(i in 1: length(year[, 1])) {
    if(year[i, ]$TMEAN > temp.max) {
      temp.max <- year[i, ]$TMEAN
      data.max[3] <- year[i, ]$Year
      data.max[2] <- year[i, ]$Month
      data.max[1] <- year[i, ]$Day
    }
  }
  #return(list(data.max, temp.max))
  return(data.max)
}
MD <- MDAT(Minusinsk.cli, 1964)
MDS <- date2string(MD)
cat("MDAT= ", MD, MDS, "\n")

```
### Main function eval16CliPars
```{r eval16CliPars}
eval16CliPars <- function(stationCode, data.cli, data.calc, beginYear, endYear) {
    period <- beginYear: endYear # the calculation of the number of observations 
    l <- length(period)
    # the creation of a matrix of l rows and 16 columns
    m16 <- matrix(c(1:(l * (16+4))), nrow = l, ncol = (16+4), byrow = TRUE)
    m16.df <- as.data.frame(m16)  #  converted to dataframe
    fistCol <- c("Station_Code", "Year", "StartD", "EndD")
    lastCol <- c("STDAT0", "STDAT5", "FDAT0", "FDAT5", "INTER0", 
        "INTER5", "MAXT", "MDAT", "SUMT0", "SUMT5", "T220", "T225", "FT220", "FT225", 
        "SPEEDT", "SUMPREC") 
    # assign names to the columns
    df16 <- setNames(m16.df, c(fistCol, lastCol))
    # the task is to determine the data type of each column
    df16$Station_Code <- as.character(df16$Station_Code)
    df16$STDAT0 <- as.character(df16$STDAT0)
    df16$STDAT5 <- as.character(df16$STDAT5)
    df16$FDAT0 <- as.character(df16$FDAT0)
    df16$FDAT5 <- as.character(df16$FDAT5)
    df16$MDAT <- as.array(df16$MDAT)
    cat("Start eval16CliPars\n")
    for (i in 1:l) {
        #cat(".")
        df16$Station_Code[i] <- stationCode
        df16$Year[i] <- period[i]
        SE <- season_growth(data.cli, period[i])
        df16$StartD[i] <- SE[1]
        df16$EndD[i] <- SE[2]
        cat("The date of transition through 0C at the beginning of the growing season STDAT0\n")
        D <- STDAT0(data.cli, data.calc, period[i])
        df16$STDAT0[i] <- date2string(D)
        cat("The date of transition through 5C in the beginning of the growing season STAT5\n")
        D <- STDAT0(data.cli, data.calc, period[i], 11)
        df16$STDAT5[i] <- date2string(D)
        cat("Date of transition at the end of the season after 0 - 5 FDAT0\n")
        D <- FDAT0(data.cli, data.calc, period[i])
        df16$FDAT0[i] <- date2string(D)
        D <- FDAT0(data.cli, data.calc, period[i], 5)
        df16$FDAT5[i] <- date2string(D)
        cat("The maximum temperature MAXT\n")
        df16$MAXT[i] <- MAXT(data.cli, period[i])
        cat("Date of the maximum temperature MDAT\n")
        D <- MDAT(data.cli, period[i])
        df16$MDAT[i] <- date2string(D)
        cat("The duration of the season from 0C to 0C, 5C to 5C INTER0\n")
        SL <- INTER0(data.cli, data.calc, period[i])
        df16$INTER0[i] <- SL
        df16$INTER5[i] <- INTER0(data.cli, data.calc, period[i], temp.c = 5)
        cat("The sum of temperatures more 0C, 5C SUMT0\n") 
        df16$SUMT0[i] <- SUMT0(data.cli, data.calc, period[i])
        df16$SUMT5[i] <- SUMT0(data.cli, data.calc, period[i], 5)
        cat("The sum of temperatures above 0C-5C until June 22 T2205\n") 
        df16$T220[i] <- T2205(data.cli, data.calc, period[i])
        df16$T225[i] <- T2205(data.cli, data.calc, period[i], 5)
        cat("The sum of temperatures from 22 June to go through 0o at the end of the season FT2205\n")
        df16$FT220[i] <- FT2205(data.cli, data.calc, period[i])
        df16$FT225[i] <- FT2205(data.cli, data.calc, period[i], temp.c = 5)
        cat("The rate of temperature rise of (Скорость подъема температуры) SPEEDT\n")
        df16$SPEEDT[i] <- SPEEDT(data.cli, period[i])
        cat("Сумма осадков в течение сезона роста\n")
        df16$SUMPREC[i] <- SUMPREC(data.cli, data.calc, period[i])
    }
    cat("\n")
    # the estimated return table from function
    return(df16)
}
```
### Results of calculation
  + Structure of the table of results
  + First 6 lines
  + Descriptive statisticians (one line one year)
  + <http://www.inp.nsk.su/~baldin/DataAnalysis/R/R-10-hpc.pdf>
  + <https://habrahabr.ru/post/168399/>
```{r}
if (.TT == TRUE) {
    require(pracma)
    tic()
    E <- eval16CliPars("23365", Minusinsk.cli, Minusinsk.cli, 1936, 2013)
    toc()
    str(E)
    head(E)
    summary(E)
}

cat("EVAL16CLIPARS Done.")

```
### Write to file - format data.frame (e16cp.csv)
```{r writenewdatasets}
# Write to file - format data.frame
write_eval_clipars <- function(filename.full, df.eval) {
    write.table(file = filename.full, df.eval, row.names = FALSE, sep = ";", quote = FALSE, 
        eol = "\n", na = "NA", dec = ",", col.names = TRUE)
}
write_eval_clipars(paste0(mm_path, '/23365.csv'), E)

```
### WriteXLSX
  + <https://github.com/stan-dev/rstan/wiki/Install-Rtools-for-Windows>
  + <https://cran.r-project.org/bin/windows/Rtools/>
  + <https://github.com/awalker89/openxlsx/issues/111>
```{r xlsx}
#install.packages('pacman', dependencies=TRUE, repos='http://cran.rstudio.com/')
#install.packages('openxlsx', dependencies=TRUE, repos='http://cran.rstudio.com/')

#Sys.setenv("R_ZIPCMD" = "C:/Rtools/bin/zip.exe") ## path to zip.exe
Sys.setenv(R_ZIPCMD = paste0(mm_path, "/bin/zip.exe"))  ## path to zip.exe
require(openxlsx)
# test data.frame's
testWriteReadXLSX <- function(listDF, fileName, sheet = 1) {
    openxlsx::write.xlsx(listDF, file = fileName)
    R <- openxlsx::read.xlsx(xlsxFile = fileName, sheet = sheet, skipEmptyRows = TRUE)
    return(R)
}
testListDF <- list(iris = iris, mtcars = mtcars, chickwts = chickwts, quakes = quakes)
WR <- testWriteReadXLSX(testListDF, paste0(mm_path, "/23365.xlsx"))
str(WR)
head(WR)
WR <- testWriteReadXLSX(list(E, testListDF[1]), paste0(mm_path, "/23365.xlsx"), sheet = 1)
str(WR)
head(WR)

```
### Summary table on climate stations
```{r master_location}
df.names <- c("Statio_Code", "Latitude", "Longitude", "Elevation", "Start_Y", " End_Y" )

st <- read.csv("master-location-identifier-database-20130801.csv", header = TRUE, sep = ",", dec = ".")

L <- length(st[, 1])
for (i in 1:L) {
    if (!is.na(st[i, 12])) {
        if (st[i, "wmo_xref"] == 23365)
            cat(i, "\n")
    }
}

```
### SysAdmins
```{r sysadmn}
# knitr: run all chunks in an Rmarkdown document                              
# http://stackoverflow.com/questions/24753969/knitr-run-all-chunks-in-an-rmarkdown-document
runAllChunks <- function(rmd, envir = globalenv()) {
    tempR <- tempfile(tmpdir = ".", fileext = ".R")
    on.exit(unlink(tempR))
    knitr::purl(rmd, output = tempR)
    sys.source(tempR, envir = envir)
    unlink(tempR)
}

#runAllChunks("transect.Rmd")
#Rmd2R("transect.Rmd", "transect.R")
```
### Tips
```{r tips}
# file:///home/larisa/Dropbox/24516/eval16clipars/e16cp.html
# require(knitr); knit2html('Z:/home/larisa/Dropbox/24516/eval16clipars/e16cp.R')
# http://master-css.com/page/brackets-code-editor
# http://www.biostat.jhsph.edu/~rpeng/docs/R-debug-tools.pdf
# http://tukachev.flogiston.ru/blog/?p=1352
# http://r-analytics.blogspot.ru/p/blog-page_20.html#.V_8uqeWLS01
#  http://kpfu.ru/docs/F568269105/metodichka_R_1.pdf
#  http://shelly.kpfu.ru/e-ksu/docs/F1594376599/%ec%e5%f2%ee%e4%e8%f7%ea%e0_R_2.pdf
#  http://herba.msu.ru/shipunov/software/r/cbook.pdf
#  http://gis-lab.info/docs/books/moskalev2010_statistical_analysis_with_r.pdf
#  https://dl.dropboxusercontent.com/u/7521662/Zaryadov%20%282010%29%20Intro%20to%20R.pdf
#  http://www.unn.ru/pages/e-library/methodmaterial/2010/3.pdf
#  http://gis-lab.info/docs/saveliev2012-geostat.pdf
#  http://www.ievbras.ru/ecostat/Kiril/Article/A32/Starb.pdf
#  http://ashipunov.info/shipunov/school/books/rbook.pdf
#  https://dl.dropboxusercontent.com/u/7521662/Saveliev_2014_Code.rar
#  https://dl.dropboxusercontent.com/u/7521662/Saveliev_2014_Point_Process.pdf
#  https://github.com/ranalytics/r-tutorials/tree/master/Edition_2015
#  http://www.ievbras.ru/ecostat/Kiril/R/Ecotox/Ecotoxicology.pdf
#  http://www.ievbras.ru/ecostat/Kiril/R/Ecotox/Scripts_data.zip
#  http://www.inp.nsk.su/~baldin/DataAnalysis/R/R-10-hpc.pdf
```




















